Analysis of Bauer et al. (unpublished) Field experiment: <br> Persistence

### 2022-12-07 R/model_recovery_check.Rmd

```{r load-models collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_recovery_full.Rdata"))
load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
m_1 <- m_full
m_2 <- mfull_prior
```

@@

### Coefficient of determination (<i>R</i>^2)

#### Conditional <i>R</i>^2 values

#### Marginal <i>R</i>^2 values

@@

## Output of choosen model

### Model output

Conditional and marignal <i>R</i>²

```{r conditional-marginal-r2 collapse = TRUE}
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula =  ~ (1 | site/plot)) 
brms::bayes_R2(m_1, probs = c(0.05, 0.5, 0.95),
         re_formula = 1 ~ 1)
```

Posteriors of chosen model

```{r posteriors-chosen-model}
draws1
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Posteriors of second model:

```{r posterors-2nd-model}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

@@

Effect sizes just to get exact values of means etc. if necessary.

>>>>

```{r load-models collapse = TRUE, message = FALSE}
load(file = here("outputs", "models", "model_recovery_full.Rdata"))
# BARG 5
load(file = here("outputs", "models", "model_recovery_full_flat.Rdata"))
# BARG 1.E
load(file = here("outputs", "models", "model_recovery_full_prior.Rdata"))
m_1 <- m_full
m_2 <- mfull_prior
```

@@

@@

## Model comparison

### Conditional <i>R</i>^2 values

### Marginal <i>R</i>^2 values

### Bayes factor (BARG 3.C)

```{r}
brms::bayes_factor(m_1, m_2)
```

## Posterior distributions (BARG 3.B)

### Forest plot

Chosen model:

```{r posteriors-chosen-model}
mcmc_intervals(
  posterior1,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

Second model:

```{r posteriors-2nd-model}
mcmc_intervals(
  posterior2,
  prob = 0.66,
  prob_outer = 0.95,
  point_est = "mean"
  ) +
  theme_classic()
```

@@

Effect sizes of chosen model just to get exact values of means etc. if necessary.
